Drake Plan

### 2020-01-11 R/drake_plan_conus.Rmd
add memory strategy

# point to cache: 
ssd_cache = drake_cache(path = "/scratch/cache/aeronet_drake")
set.seed(1234)
```

@@

```{r, eval = F}
# make(conus_plan, cache = ssd_cache)
(time0 <- Sys.time())
future::plan(future::multiprocess)
options(future.globals.maxSize= 100*1024^3) 
make(conus_plan, cache = ssd_cache,
     parallelism = "future", jobs = 20, garbage_collection = TRUE)
Sys.time() - time0

>>>>

# point to cache: 
ssd_cache = drake_cache(path = "/data-coco/mcd19/cache/aeronet_drake")
set.seed(1234)
```

@@

```{r, eval = F}
# make(conus_plan, cache = ssd_cache)
(time0 <- Sys.time())
future::plan(future::multiprocess)
options(future.globals.maxSize= 100*1024^3) 
make(conus_plan, cache = ssd_cache,
     parallelism = "future", jobs = 5, garbage_collection = TRUE, 
     keep_going = TRUE, memory_strategy = "preclean")
Sys.time() - time0
